%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

\usepackage{hyperref}

% Set applicant's personal data for header
\name{Kai Wang \linebreak \linebreak \normalsize{Aim to Solve Any Technical Problems}}
\address{Haidian District \linebreak Beijing, China}
\contacts{(+86) 13811539414 \linebreak charles.wangkai@gmail.com}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Senior Software Engineer}{BigOne Lab, China}{Dec 2017 – Oct 2019}
			Data Intelligence Platform for Key Decision Makers
			\begin{itemize}
				\item Explored and applied new methods in Tech Lab. (AWS Lambda, Google Apps Script, Slack Bot, NLP)
				\item Led the development of the web dashboard. (React, Node.js, Elasticsearch, Redis, Code Review)
				\item Developed web crawlers to extract public data. (Python, Scrapy, Reverse Engineering)
			\end{itemize}
		\end{cvsubsection}

		\begin{cvsubsection}{Big Data Engineer}{Ping++, China}{Dec 2015 – Nov 2017}
			Business Intelligence Platform to Drive Growth
			\begin{itemize}
				\item Implemented ETL, user id mapping, key metrics. (Aliyun MaxCompute, SQL, Java)
				\item Implemented a sales amount prediction application. (Machine Learning, Xgboost, Python)
				\item Restored millions of hashed IMEI ids. (Multiprocessing, Java, AWS EC2)
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Engineer}{Amazon, China}{Apr 2014 – Oct 2014}
			MFNCOD (Merchant Fulfillment Network, Cash On Delivery)
			\begin{itemize}
				\item Integrated ship track information from the carrier Best Express into Amazon China MFN. (Java, Unit Test)
				\item Enhanced the internal tool used by the operational team. (Ruby on Rails)
				\item Built data warehouse reports regularly for operational monitoring. (SQL)
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Software Engineer}{IBM, China Development Lab}{Jul 2009 – Apr 2014}
			Entitled Software (IBM Z Mainframe Software License Management)
			\begin{itemize}
				\item Redesigned the report generation pipeline, by separating the data source and transformation. (C, XML, XSLT)
				\item Initiated and developed a test data builder tool, saving manual work by 85\%. (JDBC, JSON, jQuery)
				\item Implemented a web page for displaying the decision making tree. (jsTree, Flexigrid, Single-Page Application)
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{Beijing}{Beijing University of Technology}{Sep 2002 – Jul 2009}
			\begin{itemize}
				\item Master's Degree in Computer Applied Technology, Jul 2009. GPA: 3.5
				\item Bachelor's Degree in Computer Science and Technology, Jul 2006. GPA: 3.6
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Additional Experience and Awards}
		\begin{cvsubsection}{}{}{}
			\begin{itemize}
				\item \textbf{GitHub Profile:} \url{https://github.com/charles-wangkai}
				\item \textbf{Google Code Jam (2019):} Advanced to Round 3. {\href{http://charles-wangkai.github.io/certificates/certificate_google_code_jam_2019.pdf}{Ranked 372nd}}. (ID: goalboy1015)
				\item \textbf{Facebook Hacker Cup (2019):} Advanced to Round 2. Ranked 465th. (ID: Kai)
				\item \textbf{Google Distributed Code Jam (2016):} Advanced to Round 2. Ranked 175th. (ID: goalboy1015)
				\item \textbf{\href{https://projecteuler.net}{Project Euler}:} Level 13. Solved 325 problems. (ID: goalboy)
				\item \textbf{\href{https://www.hackerrank.com/projecteuler}{HackerRank ProjectEuler+ Contest}:} Ranked top 10 out of 110000+ participants. (ID: goalboy)
				\item \textbf{Topcoder - College Tour Beijing (2008):} Second Prize. Ranked 15th. (ID: GOALBOY)
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Skills}
		\begin{cvsubsection}{}{}{}
			\begin{itemize}
				\item Java; Python; C / C++; SQL; Shell; R; Haskell
				\item Git; Web Development; Hadoop; Android / iOS Programming; WebGL
				\item Algorithms; Machine Learning
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Favorite IT Books}
		\begin{cvsubsection}{}{}{}
			\begin{itemize}
				\item ``Programming Pearls'' (Did all the exercises)
				\item ``Clean Code: A Handbook of Agile Software Craftsmanship''
				\item ``Peopleware: Productive Projects and Teams''
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}
